\Large{Research Seminar Software Science} \\ \huge{Simulation of monadic effects in Haskell}

### 2018-05-05 paper.tex
finished subsection state transformers and initiated subsection primitive parsers

    The parser of type \textit{p} takes a state represented as a string ready to be parsed and returns a list containing the value of type \textit{p} parsed from the string and a state represented again as a string that is yet to be parsed. The case when an empty list is returned is treated as a failure \cite{pearls}. On the other hand, an non-empty list is marked as a success. Lets take into consideration a transparent parser for multiplication operations.

@@

>>>>

    The parser of type \textit{p} takes a state represented as a string ready to be parsed and returns a list containing the value of type \textit{p} parsed from the string and a state represented again as a string that is yet to be parsed. Since a parser may not consume all of its input string, the unconsumed suffix of the input must be returned along with the prefix of the input. As a result, the outcome of a parser must be a list enclosing consumed and unconsumed part of the input string. Additionally, the case when an empty list is returned is treated as a failure \cite{pearls}. On the other hand, an non-empty list is marked as a success. Lets take into consideration a straightforward parser for multiplication operations.

@@

    \subsection{Primitive Parsers}
